TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages

### 2021-04-07 article.tex
TTT: computational details

\section*{Computational details}

\begin{leftbar}
If necessary or useful, information about certain computational details
such as version numbers, operating systems, or compilers could be included
in an unnumbered section. Also, auxiliary packages (say, for visualizations,
maps, tables, \dots) that are not cited in the main text can be credited here.
\end{leftbar}

@@

Python.3.6.8-labo: 1368.6 segundos
Python.3.6.9-casa:

R-labo.3.4.4: Corriendo

The results in this paper were obtained using
\proglang{R}~3.4.1 with the
\pkg{MASS}~7.3.47 package. \proglang{R} itself
and all packages used are available from the Comprehensive
\proglang{R} Archive Network (CRAN) at
\url{https://CRAN.R-project.org/}.

@@

\begin{leftbar}
All acknowledgments (note the AE spelling) should be collected in this
unnumbered section before the references. It may contain the usual information
about funding and feedback from colleagues/reviewers/etc. Furthermore,
information such as relative contributions of the authors may be added here
(if any).
\end{leftbar}

\newpage
%% -- Bibliography -------------------------------------------------------------
%% - References need to be provided in a .bib BibTeX database.
%% - All references should be made with \cite, \citet, \citep, \citealp etc.
%%   (and never hard-coded). See the FAQ for details.
%% - JSS-specific markup (\proglang, \pkg, \code) should be used in the .bib.
%% - Titles in the .bib should be in title case.
%% - DOIs should be included where available.

>>>>

\section*{Computational details}
% 
% \begin{leftbar}
% If necessary or useful, information about certain computational details
% such as version numbers, operating systems, or compilers could be included
% in an unnumbered section. Also, auxiliary packages (say, for visualizations,
% maps, tables, \dots) that are not cited in the main text can be credited here.
% \end{leftbar}

\begin{description}
 \item[Labo] RAM 15.6G, Intel i5-3330, CPU 3.00GHz, cache 6144KB
 \item[Home] RAM 3.3G, AMD A4-6210, CPU 1.00GHz, cache 2048 KB
\end{description}

En julia con \texttt{@time}
En python fue analizado con timeit
En R con microbenchmarck

Game 2vs2:

Python.3.6.9-casa (trueskill): 0.00145

Julia.1.5.0-casa:  0.000064
Python.3.6.9-casa: 0.00014
R.3.4.4-casa:      0.03715286

Game 1vs2vs1:

Python.3.6.9-casa (trueskill):0.00245

Julia.1.5.0-casa:  0.000096
Python.3.6.9-casa: 0.00093
R.3.4.4-casa: 0.3603933

History:

Initialization:

Julia.1.5.0-casa:  0.000309
Python.3.6.9-casa: 0.001086
R.3.4.4-casa: 0.2628356

Iteration:
Julia.1.5.0-casa: 0.000582

Skill evolution, Initialization:

Julia.1.5.0-casa:  0.038117
Python.3.6.9-casa: 0.38026
R.3.4.4-casa: 93 segundos

Skill evolution, iteration:
Julia.1.5.0-casa:  0.07570
Python.3.6.9-casa: 0.87625
R.3.4.4-casa: 149 segundos

ATP:

@@

Python.3.6.8-labo: 1368.6 segundos
Python.3.6.9-casa: 4498.8 segundos

R.3.4.4-labo: exede la RAM
% 
% The results in this paper were obtained using
% \proglang{R}~3.4.1 with the
% \pkg{MASS}~7.3.47 package. \proglang{R} itself
% and all packages used are available from the Comprehensive
% \proglang{R} Archive Network (CRAN) at
% \url{https://CRAN.R-project.org/}.

@@

% \en{We thank the anonymous reviewers for their helpful feedback.}
% \es{Agradecemos a revisores anónimos por su valiosos aportes.}
%
\en{Special thanks to Heungsub Lee for having published the basic TrueSkill model in Python.}
\es{Agradecemos especialmente a Heungsub Lee por haber publicado el modelo básico de TrueSkill en Python.}
% https://github.com/sublee/trueskill/issues/14
\en{We also thank Matias Mazzanti for constructive discussions during the implementation of the method.}
\es{También agradecemos a Matias Mazantti por las discusiones constructivas durante la implementación del método.}
%
\en{This work is supported by Universidad de Buenos Aires (UBACyT \todo{ubacyt}), CONICET (\todo{conicet}), and ANPCyT (\todo{ANPCyT}).}
\es{Este trabajo fue apoyado por la Universidad de Buenos Aires (UBACyT \todo{ubacyt}), CONICET (\todo{conicet}), and ANPCyT (\todo{ANPCyT}).}

%\newpage
%% -- Bibliography -------------------------------------------------------------
%% - References need to be provided in a .bib BibTeX database.
%% - All references should be made with \cite, \citet, \citep, \citealp etc.
%%   (and never hard-coded). See the FAQ for details.
%% - JSS-specific markup (\proglang, \pkg, \code) should be used in the .bib.
%% - Titles in the .bib should be in title case.
%% - DOIs should be included where available.
